Early Observations of the Type Ia Supernova \abc:\\ Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-08-21 doc/ms.tex
Update author list

\author{S.~Dhawan}
\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{R.~Ferretti}
\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}

@@

\author{C.~Fremling}
\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{A.~Goobar}
\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}

@@

% \author[0000-0001-5807-7893]{C.~McCully}
% \affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
% \affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}

@@

\author{J.~Sollerman}
\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{F.~Taddia}
\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}

>>>>

\author{S.~Dhawan}
\affil{The Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{R.~Ferretti}
\affil{The Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}

@@

\author{C.~Fremling}
\affil{The Oskar Klein Centre, Department of Astronomy, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{A.~Goobar}
\affil{The Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}

@@

\author[0000-0001-5807-7893]{C.~McCully}
\affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
\affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}

@@

\author{J.~Sollerman}
\affil{The Oskar Klein Centre, Department of Astronomy, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{F.~Taddia}
\affil{The Oskar Klein Centre, Department of Astronomy, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}
